---
title: "Predicting Bechdel Test Results through Statistical Modeling"
author: 
  - name: "Hailey Quintavalle"
  - name: "Advisor: Matt Higham"
date: 05/10/2024
date-format: "MMM D, YYYY"
format: 
  pdf:
    toc: true
    include-in-header:
        text: |
          \usepackage{lipsum}
          \usepackage{setspace}
          \onehalfspacing
          \linespread{2}
---

```{r echo = F, warning = F, message = F}
library(tinytex)
library(tidyverse)
library(modelr)
library(broom)
basics_movies <- read_csv(here::here("data/basics_movies.csv"))
```

```{r}
#| label: setup
#| include: false

chunk_hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- chunk_hook(x, options)
  paste0("\\linespread{0.9}\n", x, "\n\n\\linespread{2}")
})
```

\pagebreak

# Abstract 

The Bechdel Test is a simple measurement designed to analyze the representation of women in film. To pass, a movie must have two female characters who have a conversation that is not about a man. The present research aims to use genre, release year, movie budget, user ratings, and critics rating scores to predict the probability a movie will pass the test. Logistic regression analysis reveals more recent movies are predicted to have a higher probability of passing the test. For most years, genres such as Romance and Comedy are predicted to have a higher probability of passing, while genres such as Action, Sport, War, and Western are predicted to have a lower probability of passing the test. Although the Bechdel Test has its flaws, the test is a useful metric to bring attention to the roles women hold in film. 


\pagebreak


# Introduction

If you think of your all-time favorite movie, try to think about how many of the main characters were women. In 2023, 35% of all speaking roles in movies belonged to women, and only 28% of the top grossing films contained female protagonists (Lauzen, 2024). Just one decade before, in 2013, women occupied 30% of all speaking roles and just 15% of protagonists were women (Lauzen, 2014). This is a small change for a span of 10 years, showcasing the underrepresentation of women in film, and the slow steps towards progress the film industry seems to be taking. As we examine the portrayal of women's roles in film, it is useful to explore various criteria used to measure their representation. One notable measure is the Bechdel Test, unintentionally introduced by American cartoonist Alison Bechdel in 1986, and the primary measure of women in film that is the focus of the present analysis. 

The Bechdel Test originated from a comic strip titled "The Rule", a part of her comic *Dykes To Watch Out For*. The comic depicts two women discussing certain criteria necessary for them to watch a movie. The criteria for a movie included: two named women, who talked to each other, and held a conversation with each other that was not about a man. In the early 2000s, the test quickly gained popularity online and has since been used as a common tool for analyzing the role of women in film. 

The test has only three basic requirements, meaning that a film can pass with just one line. Because of the simplicity of this tool, many have come forward with fair criticisms of the test. For example, the test does not take into account demographic factors, such as age, the voices of women of color, or those who do not speak English as their first language (O’Meara, 2016). Other flaws of the test include the oversight of conversations that are not directly about a man, but may be indirectly about them, where the conclusion of the test are unclear. 

Regardless of its flaws, the Bechdel Test is a straightforward and easy tool that allows people to quickly make base assumptions about the presence of women in film. For this reason, this analysis will be examining the characteristics of thousands of movies in an attempt to use logistic regression analysis to model the likelihood of passing the Bechdel Test.


## Data

The data used for the present analysis comes from a combination of multiple online sources. A data set containing 10,183 movie titles was available through IMDb Non-Commercial Datasets. Release dates for these movies range from 1874 to 2023. Variables included in this data set can be seen in the preview of the data below. 

IMDb Non-Commercial Data set:

```{r echo = F, warning = F, message = F}
basics_movies |> 
  slice(10138:10142) |>
  select(tconst, originalTitle,
         startYear, runtimeMinutes, genres) |> 
  knitr::kable() 
```

The code manual for the data from IMDb: 

 - **tconst**: alphanumeric unique identifier of the title
 
 - **originalTitle**: title of the movie
 
 - **startYear**: release year of the movie
 
 - **runtimeMinutes**: runtime in minutes
 
 - **genres**: up to three genres associated with the title


Other data that was used in this analysis comes from the Bechdel Test Movie List, where users can submit movies with their Bechdel test rating through their online platform. The data set pulled from this website contains 10,251 movies with release dates ranging from 1874 to 2024. For the rating variable, a movie is given a rating from one to three, directly corresponding with the number of requirements of the Bechdel test that it passes. Only movies with a `3` for this variable fully pass the Bechdel test. A preview of this data can be shown below.

```{r message = F, warning = F, echo = F}
movies_api <- read_csv("data/movies_api.csv")
movies_api |> 
  slice(10231:10236) |> 
  knitr::kable() 
```

The code manual for the Bechdel Test Movie List data:

- **id**: ID number

- **title**: title of the movie

- **imdbid**: IMDb number ID

- **year**: release year

- **rating**: Bechdel Test rating (0-3)

The data from IMDb Non-Commercial Datasets was joined with the data set pulled from the Bechdel test movie list to be used in the final model concerning genres. 

The final data set that was used in this analysis comes from the [TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-09/readme.md) social data project through GitHub. This data set contains 1,794 movies released from 1970 up to 2013.


```{r message = F, warning = F, echo = F}
movies <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/movies.csv')
```



```{r echo = F}
movies |> select(year, imdb, title, test, clean_test, binary, budget) |> 
  slice(44:46) |>  knitr::kable() 

movies |> select(domgross, intgross, code, budget_2013, domgross_2013, intgross_2013) |> 
  slice(44:46) |>  knitr::kable() 

movies |> select(period_code, decade_code, imdb_id, rated, language, runtime, imdb_votes) |> 
  slice(44:46) |>  knitr::kable() 

movies |> select(plot) |> 
  slice(44:46) |>  knitr::kable() 

movies |> select(writer) |> 
  slice(44:46) |>  knitr::kable()

movies |> select(country, metascore, imdb_rating, director, released, type) |> 
  slice(44:46) |>  knitr::kable() 

movies |> select(actors, genre, awards) |> 
  slice(44:46) |>  knitr::kable() 
```

The code manual for the TidyTuesday data: 

- **year**: release year

- **imdb**: IMDb id

- **title**: title of movie

- **test**: Bechdel Test outcome

- **clean_test**: Bechdel Test outcome (cleaned)

- **binary**: binary Pass or Fail of the Bechdel Test

- **budget**: budget as of release year

- **domgross**: domestic gross in release year

- **intgross**: international  gross in release year

- **code**: code for movie; contains year and Bechdel Test result

- **budget_2013**: budget normalized to 2013

- **domgross_2013**: domestic gross normalized to 2013

- **intgross_2013**: international gross normalized to 2013

- **period_code**: period code

- **decade_code**: decade code

- **imdb_id**: IMDb ID

- **rated**: content rating of movie

- **language**: language of movie
 
- **runtime**: runtime in minutes

- **plot**: plot summary of the movie

- **writer**: writer of the film

- **country**: country movie is produced in

- **metascore**: Metascore (critic) rating (0-100)

- **imdb_rating**: IMDb (user) rating (0-10)

- **director**: Director(s) of movie

- **released**: released date

- **imdb_votes**: number of IMDb votes

- **actors**: main actors in movie

- **genre**: genre

- **awards**: awards won

- **type**: type of film


## Exploratory Overview


Looking into the IMDb movie data set, the overall percentage of movies that pass the Bechdel Test is 57.0%, with the remaining 43.0% failing the test. The plot below demonstrates the proportion of movies that pass and fail the test each year, starting in 1930 up to 2023. The movies released in the years before 1935 have been excluded from this plot because of the amount of variation coming from a small number of movies each year, with an average of around 4 movies per year. 

```{r warning = F, message = F}
basics_movies |>
  mutate(binary = if_else(rating == 3, "Pass", "Fail")) |>
  select(year, binary) |>
  group_by(year, binary) |>
  summarise(n = n()) |>
  filter(year >= 1935) |> 
  pivot_wider(names_from = binary, values_from = n) |>
  mutate(Pass = if_else(is.na(Pass), 0, Pass),
         Fail = if_else(is.na(Fail), 0, Fail)) |>
  mutate(total_movies = sum(Pass, Fail)) |>
  mutate(Fail = Fail / total_movies,
         Pass = Pass / total_movies) |>
  pivot_longer(c(Fail, Pass), names_to = "binary", values_to = "prop") |>
  ggplot(aes(x = year, y = prop)) +
  geom_line(aes(color = binary), linewidth = 0.7, alpha = 0.7) +
  geom_smooth(aes(color = binary), se = F) +
  scale_color_viridis_d(name = "Test Outcome") +
  labs(x = "Year",
       y = "Proportion of Movies",
       title = "Bechdel Test Outcome Over Time") +
  theme_minimal()
```

As seen in this plot, the proportion of movies passing and failing the test has much variation from the 1930s up until the early 90s. The solid lines in the plot represent the average proportion of movies that pass and fail each year. From these lines it is apparent that a greater proportion of movies had failed every year until the early 90s. After this point, however, the proportion of movies that pass each year appears to grow at a steady rate.

The following plot shows the proportion of films that pass and fail the Bechdel Test within each movie genre. The blue line represents the point of indifference where half of the movies pass and half fail. 

```{r}
# movies appear multiple times for multiple listed genres
movies_model <- basics_movies |> separate_rows(genres, sep = ",") 
movies_model <- movies_model |> mutate(binary = if_else(rating == 3, "1", "0")) |> 
  mutate(binary = as.numeric(binary)) |>
  filter(!genres %in% c("News", "Adult", "Talk-Show", "\\N")) |>
  relocate(binary)

```

```{r message = F, warning = F}
basics_movies |>
  mutate(binary = if_else(rating == 3, "Pass", "Fail")) |>
  separate_rows(genres, sep = ",") |>
  select(genres, binary) |>
  group_by(genres, binary) |>
  summarise(n = n()) |>
  filter(n > 4) |>
  pivot_wider(names_from = binary, values_from = n) |>
  mutate(Pass = if_else(is.na(Pass), 0, Pass),
         Fail = if_else(is.na(Fail), 0, Fail)) |>
  mutate(total_movies = sum(Pass, Fail)) |>
  mutate(Fail = Fail / total_movies,
         Pass = Pass / total_movies) |>
  pivot_longer(c(Fail, Pass), names_to = "binary", values_to = "prop") |>
  filter(genres != "NA",
         genres != "Film-Noir",
         genres != "Adult") |>
  ggplot(aes(x = genres, y = prop)) +
  geom_col(aes(fill = binary), position = "stack") +
  geom_hline(yintercept = 0.5, linewidth = 1.2, color = "lightseagreen") +
  theme_minimal() +
  labs(x = "Genres",
       y = "Proportion of Movies",
       title = "Bechdel Test Outcome in Each Genre") +
  scale_fill_viridis_d(name = "Test Outcome") +
  coord_flip()
```

As can be seen from this plot, most genres tend to have a higher proportion of movies that pass the test, with few genres falling far below 50%. 

Exploring the TidyTuesday data set allows us to examine other characteristics of movies, such as movie budget and different types of ratings. The plot below shows the difference in critic ratings, or Metascore, between movies that pass and fail the Bechdel Test. 

```{r message = F, warning = F}
movies |>
  ggplot(aes(x = binary, y = metascore)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Bechdel Test Outcome", 
       y = "Metascore",
       title = "Bechdel Test Rating and Critic Ratings")
```

The plot above suggests a slight increase in average Metascore ratings for the movies that do not pass the Bechdel Test, but the difference appears to be too small to be notable. Demonstrated in the following plot, movies that do not pass the Bechdel Test also appear to have higher average user ratings than movies that pass.


```{r message = F, warning = F}
movies |>
  ggplot(aes(x = binary, y = imdb_rating)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Bechdel Test Outcome", 
       y = "IMDb Rating",
       title = "Bechdel Test Rating and User Ratings")
```

In terms of movie budget, it appears that movies that fail tend to show larger movie bugdets than movies that pass the test, as shown in the following plot. 

```{r message = F, warning = F}
movies |>
  ggplot(aes(x = binary, y = budget_2013)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Bechdel Test Outcome", 
       y = "Budget",
       title = "Bechdel Test Rating and Movie Budget")
```

Another interesting variable in this data set is content rating. The content rating is designed to classify movies based on the audiences they are suitable for, based on factors like profanity, violence, sexual content, substance use, and any other topics that are not recommend for children to watch. The plot below contains five different content ratings with the proportion of movies that pass and fail the Bechdel Test in those categories. 


```{r message = F, warning = F}
movies |>
  select(rated, binary) |>
  group_by(rated, binary) |>
  summarise(n = n()) |>
  filter(n > 4) |>
  pivot_wider(names_from = binary, values_from = n) |>
  mutate(Pass = if_else(is.na(PASS), 0, PASS),
         Fail = if_else(is.na(FAIL), 0, FAIL)) |>
  mutate(total_movies = sum(Pass, Fail)) |>
  mutate(Fail = Fail / total_movies,
         Pass = Pass / total_movies) |>
  pivot_longer(c(Fail, Pass), names_to = "binary", values_to = "prop") |>
  filter(rated != "N/A") |>
  ggplot(aes(x = rated, y = prop)) +
  geom_col(aes(fill = binary), position = "stack") +
  geom_hline(yintercept = 0.5, linewidth = 1.2, color = "lightseagreen") +
  theme_minimal() +
  labs(x = "Content Rating",
       y = "Proportion of Movies",
       title = "Bechdel Test Outcome and Content Rating") +
  scale_fill_viridis_d(name = "Test Outcome")
```

The blue line represents the point of indifference, where the proportion of movies that pass is equal to 50%. The proportion of movies that pass the test does not reach half for any of the content rating categories, revealing that the majority of movies in each of these categories do not seem to pass. 



# Modeling

## Genre Analysis

The goal of this analysis is to determine which genres have a higher likelihood of passing the Bechdel Test, and how that trend varies over time. To do this, a logistic regression model was created to model this probability, using all genres provided by the data and their interactions with release year. The full model with all coefficients is shown below. This model was created using the data from the IMDb database and the Bechdel Test Movie List. 
 
$$
\text{logit}(\pi) = \beta_0 + \beta_1 \cdot \text{Year} + \beta_2 \cdot \text{Animation} + \beta_3 \cdot \text{Action} + \beta_4 \cdot \text{Adult} \\
$$
$$
+ \beta_5 \cdot \text{Adventure} + \beta_6 \cdot \text{Biography}
+ \beta_7 \cdot \text{Comedy} + \beta_8 \cdot \text{Crime} 
+ \text{ } \beta_9 \cdot \text{Documentary}
$$
$$
 + \beta_{10} \cdot \text{Drama} + \beta_{11} \cdot \text{Family} 
+ \beta_{12} \cdot \text{Fantasy} + \text{ } \beta_{13} \cdot \text{History} + \beta_{14} \cdot \text{Horror} 
$$
$$
+ \beta_{15} \cdot \text{Music} + 
 \beta_{16} \cdot \text{Musical} + \text{ } \beta_{17} \cdot
 \text{Mystery} + \beta_{18} \cdot \text{Romance} + \beta_{19} \cdot \text{Short} 
$$
$$
+ \beta_{20} \cdot \text{Sport} 
+ \text{ } \beta_{21} \cdot \text{Thriller} + \beta_{22} \cdot \text{War} + \beta_{23} \cdot \text{Western}
$$
$$
+ \text{ } \beta_{24} \cdot \text{Year:Animation} + \beta_{25} \cdot 
\text{Year:Action} + \beta_{26} \cdot \text{Year:Adult} + \text{ } 
\beta_{27} \cdot \text{Year:Adventure} 
$$
$$
+ \beta_{28} \cdot \text{Year:Biography} + \beta_{29} \cdot \text{Year:Comedy}
+ \text{ } \beta_{30} \cdot \text{Year:Crime} + \beta_{31} \cdot \text{Year:Documentary} 
$$
$$
+ \beta_{32} \cdot \text{Year:Drama} + \text{ } \beta_{33} \cdot \text{Year:Family} + \beta_{34} \cdot \text{Year:Fantasy} + \beta_{35} \cdot \text{Year:History} 
$$
$$
+ \text{ } \beta_{36} \cdot \text{Year:Horror} + \beta_{37} \cdot \text{Year:Music} + \beta_{38} \cdot \text{Year:Musical}+ \text{ } \beta_{39} \cdot \text{Year:Mystery} 
$$
$$
+ \beta_{40} \cdot \text{Year:Romance} + \beta_{41} \cdot \text{Year:Short}
+ \text{ } \beta_{42} \cdot \text{Year:Sport} + \beta_{43} \cdot \text{Year:Thriller} 
$$
$$
+ \beta_{44} \cdot \text{Year:War} + \beta_{45} \cdot \text{Year:Western}
$$

Within this model, $\pi$ represents the probability of passing the test and $logit(\pi)$ represents the log odds of passing the test. Each genre in the present model is an indicator variable, with values 1 and 0 representing if the movie is that genre or not, respectively. For example, if a movie is an action film, the Action term in the model would be the value 1. If a different movie is entered in the model and not considered an action film, then the Action term would be 0. Interaction terms allow for the association between the log odds of passing the test and time to be different for different genres. Each $\beta$ value with its statistical significance is shown in the table below. 

```{r message = F, warning = F, cache = T, out.width='100%'}
## basics_movies with indicator variable for each genre
movies_indi <- read_csv(here::here("data/movies_indicator.csv")) 

new_grid <- read_csv(here::here("data/movies_grid1.csv"))
library(modelr)
library(broom)

genre_model <- glm(factor(binary) ~ year + Animation + Action + Adult + 
                     Adventure + Biography + Comedy + Crime + 
                     Documentary + Drama + Family + Fantasy + 
                     History + Horror + Music + Musical +
                     Mystery + Romance + Short + Sport + 
                     Thriller + War + Western + year:Animation + 
                     year:Action + year:Adult + year:Adventure + 
                     year:Biography + year:Comedy + year:Crime +
                     year:Documentary + year:Drama + year:Family +
                     year:Fantasy + year:History + year:Horror + 
                     year:Music + year:Musical + year:Mystery + 
                     year:Romance + year:Short + year:Sport + 
                     year:Thriller + year:War + year:Western,
                   family = "binomial", data = movies_indi)
```


```{r echo = F}
genre_model |> pander::pander(caption = "Logistic Model Coefficients")
```

To understand the relationship between specific genres and likelihood of passing of the Bechdel Test, individual coefficients for selected genres can be interpreted. For a one year increase in release year, the log odds is predicted to increase by 0.030 (0.01908 + 0.01093 = 0.03001) when the movie is considered an adventure film. This relationship has been proven to be statistically significant, with a p-value of 0.001. For animated movies, a one year increase in release year means the log odds is predicted to increase by 0.031 (0.01908 + 0.01204 = 0.031), with a p-value of 0.028. For western movies, a one year increase in release year results in a predicted 0.007 (0.01908 - 0.01187 = 0.00721) increase in log odds, a much slower rate than most other movie genres. 

The following plots showcase these relationships well, along with the other genres included in the model. Each colored trend line represent a different movie genre, with year along the x-axis and the predicted probability of passing the Bechdel Test on the y-axis. The tick marks along the top and bottom of the plots represent the movies that pass and fail each year respectively. Each plot contains a different group of genres. The genres were plotted on multiple graphs for clarity. 

```{r}
aug_mod3 <- augment(genre_model, newdata = new_grid, se_fit = TRUE)

aug_mod3 <- aug_mod3 |> mutate(.pi = exp(.fitted) / (1 + exp(.fitted)))

list3 <- aug_mod3 |> pivot_longer(cols = c(Animation, Action, Adult, 
                                           Adventure, Biography, Comedy, 
                                           Crime, Documentary, Drama, 
                                           Family, Fantasy, History, 
                                           Horror, Music, Musical, Mystery,
                                           Romance, Short, 
                                           Sport, Thriller, 
                                           War, Western), names_to = "genre", 
                                  values_to = "values")

movies_pass <- movies_indi |> filter(binary == 1)
movies_fail <- movies_indi |> filter(binary == 0)
```



```{r}
list3 |> filter(values == 1, genre %in% 
                  c("Sport", "Comedy", "Romance", "Adventure",
                    "Documentary", "War", "Western")) |> 
  mutate(genre = fct_reorder2(genre, .x = year, .y = .pi)) |>
  ggplot(aes(x = year, y = .pi)) +                      
  geom_line(aes(color = genre), linewidth = 0.9) + 
  geom_rug(data = movies_pass,
           aes(x = year, 
               y = as.numeric(binary)), 
           sides = "t", alpha = 0.1) +
  geom_rug(data = movies_fail,
           aes(x = year, 
               y = as.numeric(binary)), 
           sides = "b", alpha = 0.1) +  
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     limits = c(0, 1)) + 
  theme_minimal() +
  labs(x = "\nYear",
       y = "Probabilty of Passing\n", 
       color = "Genre",
       title = "Different Genres Over Time") +
  scale_color_viridis_d()
```

In the previous plot, the predicted probability of passing the test appears to be lower for genres such as war and western movies, and appears to be the highest for romance, adventure, and comedy movies. The strongest increase in predicted probability over time seems to be adventure movies, as the trend line begins close to 0 in the late 1800s and climbs to almost 75% in recent years.


```{r}
list3 |> filter(values == 1, genre %in% 
                  c("Horror", "Family", "Fantasy", "Drama",
                    "Animation", "Crime", "Sci-Fi", "Musical")) |> 
  mutate(genre = fct_reorder2(genre, .x = year, .y = .pi)) |>
  ggplot(aes(x = year, y = .pi)) +                      
  geom_line(aes(color = genre), linewidth = 0.9) + 
  geom_rug(data = movies_pass,
           aes(x = year, 
               y = as.numeric(binary)), 
           sides = "t", alpha = 0.1) +
  geom_rug(data = movies_fail,
           aes(x = year, 
               y = as.numeric(binary)), 
           sides = "b", alpha = 0.1) +  
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     limits = c(0, 1)) + 
  theme_minimal() +
  labs(x = "\nYear",
       y = "Probabilty of Passing\n", 
       color = "Genre",
       title = "Different Genres Over Time") +
  scale_color_viridis_d()

```

This plot clearly demonstrates the relationship found between Bechdel Test results and animated movies, similar to that of the one seen in adventure movies. The trend line representing the animation genre appears to show the steepest climb of the genres presented in this visual, possibly signifying animated movies have seen a faster progression of including female roles in film over time than other genres included in this analysis. 


```{r}
list3 |> filter(values == 1, genre %in% 
                  c("Thriller", "Biography", "Mystery", "History",
                    "Short", "Action")) |> 
  mutate(genre = fct_reorder2(genre, .x = year, .y = .pi)) |>
  ggplot(aes(x = year, y = .pi)) +                      
  geom_line(aes(color = genre), linewidth = 0.9) + 
  geom_rug(data = movies_pass,
           aes(x = year, 
               y = as.numeric(binary)), 
           sides = "t", alpha = 0.1) +
  geom_rug(data = movies_fail,
           aes(x = year, 
               y = as.numeric(binary)), 
           sides = "b", alpha = 0.1) +  
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     limits = c(0, 1)) + 
  theme_minimal() +
  labs(x = "\nYear",
       y = "Probabilty of Passing\n", 
       color = "Genre",
       title = "Different Genres Over Time") +
  scale_color_viridis_d()
```

From this final plot it can be noted that the predicted probability of short films and action films have experienced a similar, but steep increase from the 1900s to today. The other genres included here show a steady increase of probability over time. 


## Rating Analysis


Since the TidyTuesday data contained a variety of movie characteristics that is not provided by IMDb or the Bechdel Test Movie List, it was used in a logistic regression model constructed to investigate the effects of movie budget, year, IMDb rating, and Metascore rating on a movie's likelihood of passing the Bechdel Test. The full model with all coefficients is shown below. The cost of the budget has been normalized to 2013, as this is where the data set ends. 


$$
logit(\pi) = \beta_0 + \beta_1 \cdot \text{Budget} + \beta_2 \cdot \text{Year} + \beta_3 \cdot \text{IMDb Rating} +  \text{ } \beta_4 \cdot \text{Metascore}
$$

Similar to the model created in the previous section, $\pi$ represents the probability of passing the Bechdel Test and $logit(\pi)$ represents the log odds of passing the test. The $\beta$ values of this model with the statistical significance for each is shown in the table below. 


```{r}
movies <- movies %>% mutate(binary_0 = ifelse(binary == "PASS", 1, 0))

mod_year <-  glm(binary_0 ~  budget_2013 +
                  year + 
                  imdb_rating +                 
                  metascore,                     
                data = movies, family = "binomial") 
```

```{r echo = F}
mod_year |> pander::pander(caption = "Logistic Model Coefficients")
```

Interpreting the coefficient values produced by the logistic regression can be helpful in understanding their relationship with Bechdel Test outcome. For example, the value of the coefficient for budget is -6.397e-09, indicating a negative relationship between budget and passing the Bechdel Test. In other words, movies with higher budgets tend to be less likely to pass the Bechdel Test. A seen by the very small p-value, this relationship reveals to be significant.

Among the other predictors, IMDb rating and Metascore also demonstrate significant relationships when predicting Bechdel Test outcome. The model output reveals that when the IMDb rating of a movie increases by 1 point, the log odds of a movie passing the test decreases by 0.562, when all other variables are held constant. This signifies that movies that pass the Bechdel Test tend to have lower ratings on IMDb, confirming what was observed in the exploratory analysis. In contrast, the relationship between critic rating and Bechdel Test outcome appears to show the opposite effect. As the Metascore rating for a movie increases by 1 point, the log odds of a movie passing the test increases by 0.017, meaning that movies that pass the Bechdel Test are predicted to have higher critic ratings. 

The last predictor in this model is year, predicting that as the release year increases by 1, the log odds of passing the test increase by 0.015 as other variables are held constant. This demonstrates that newer movies are more likely to pass the test than older movies.

The following plot visualizes this model using year, Metascore, and IMDb ratings to predict the probability that a movie will pass the Bechdel Test. 

```{r}
grid <- movies |>
  data_grid(
    year = seq_range(year, n = 4),
    binary_0 = c(0, 1),
    imdb_rating = seq_range(imdb_rating, n = 6),
    budget_2013 = median(movies$budget_2013, na.rm = T),
    metascore = seq_range(metascore, n = 4)
    )

aug_year <- augment(mod_year, newdata = grid, se_fit = TRUE)
aug_year <- aug_year |> mutate(.pi = exp(.fitted) / (1 + exp(.fitted))) |> 
  mutate(year = round(year, 0))
```



```{r}
ggplot(data = aug_year, aes(x = metascore, y = .pi)) +
  geom_line(aes(color = as.factor(round(imdb_rating))), linewidth = 1) +
  facet_wrap(~ year) + 
  labs(y = "Probability of Passing Test",
       x = "Metascore", 
       title = "Ratings and Budget Over Time") +
  scale_color_viridis_d(name = "IMDB Rating") +
  theme_minimal()
```

From this plot we can observe how movies rated lower on IMDb tend to have a higher predicted probability of passing the test. This is shown through the different colored trend lines representing IMDb ratings, as lower lines representing lower ratings appear towards higher probabilities. Furthermore, the upward direction of the lines in the plot visualize how movies with higher critic ratings have a higher predicted probability of passing the Bechdel Test. Lastly, the plot is split into four different graphs to represent the change in probability over time. The difference appears to be small, but predicted probability increases when moving from past to present years. 


# Conclusion

Overall, this analysis was designed to investigate the Bechdel Test, a test created to assess the roles of women in film. To pass this test a movie needs to have two named female characters who have a conversation that is not about a man. Characteristics that were included in this analysis were genre, release year, IMDb rating, Metascore, and movie budget. Within the genre analysis it was found that some genres are predicted to pass the test across time more than other genres such as romance, adventure, and comedy movies. Movies genres that had the least predicted probability of passing included sport, western, and war movies. Further analysis concluded that movies with lower budgets have a higher predicted probability of passing the Bechdel Test. Movies with lower user ratings through IMDb were also more likely to pass the Bechdel Test, but movies with higher critic ratings were more likely to pass the test. 


## Limitations

One limitation of the present study is that the data used for the ratings analysis only contained movies up to 2013, so conclusions about movie budget and ratings from 2013 to 2023 were unable to be drawn. Additionally, it should be noted that the Bechdel Test Movie List consists of movies reported by online users, and therefore may contain the most popular films that are most likely to be reported. 


## Future Work

Exploring additional variables beyond those examined in the current analysis could provide deeper insights into the determinants of Bechdel Test outcomes. For instance, future research might consider factors such as content rating, the number of awards and nominations received by a film, or characteristics of the director, including gender. Additionally, alternative metrics for assessing women's representation in film, such as the number of lines spoken by female characters or the presence of female protagonists, could offer alternative perspectives. As women's roles in film evolve, it's crucial for those responsible to be held accountable for their inclusion. Research such as the present analysis helps to raise awareness of the presence of women and advocate for meaningful progress within the film industry. 


# References

1. Bechdel, A. (1986). Dykes to watch out for. *Firebrand Books*.


2. Lauzen, M. (2024). It’s a Man’s (Celluloid) World: Portrayals of female characters in the top grossing U.S. Films of 2023. *Center for the Study of Women in Television & Film*. https://womenintvfilm.sdsu.edu/its-a-mans-celluloid-world-portrayals-of-female-characters-in-the-top-grossing-u-s-films-of-2023/ 


3. Lauzen, M. (2014). It’s a Man’s (Celluloid) World: On-Screen Representations of Female Characters in the Top 100 Films of 2013. *Center for the Study of Women in Television & Film*. https://womenintvfilm.sdsu.edu/files/2013_It’s_a_Man’s_World_Report.pdf 










