---
title: "Predicting Bechdel Test Results through Statistical Modeling"
format: gfm
---


```{r echo = F, warning = F, message = F}
library(tinytex)
library(tidyverse)
library(modelr)
library(broom)
basics_movies <- read_csv(here::here("data/basics_movies.csv"))
movies <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/movies.csv')
```


## Introduction

As we examine the portrayal of women's roles in film, it is useful to explore various criteria used to measure their representation. One notable measure is the Bechdel Test, unintentionally introduced by American cartoonist Alison Bechdel in 1986, and the primary measure of women in film that is the focus of the present analysis. To pass the test, the movie must contain two named women, who have a conversation with each other that is not about a man. The Bechdel Test is a straightforward and easy tool that allows people to quickly make base assumptions about the presence of women in film. For this reason, this project will be examining the characteristics of thousands of movies in an attempt to use logistic regression analysis to model the likelihood of passing the Bechdel Test. 

## Data

The final data set used in the analysis was available through [IMDb Non-Commercial Datasets](https://developer.imdb.com/non-commercial-datasets/) and the [Bechdel Test Movie List](https://bechdeltest.com/), containing 10,183 movie titles released from 1874 to 2023. 

```{r}
basics_movies |> 
  slice(10138:10142) |>
  select(tconst, originalTitle,
         startYear, runtimeMinutes, genres, rating) |> 
  knitr::kable() 
```

The code manual for the data from IMDb: 

 - **tconst**: alphanumeric unique identifier of the title
 
 - **originalTitle**: title of the movie
 
 - **startYear**: release year of the movie
 
 - **runtimeMinutes**: runtime in minutes
 
 - **genres**: up to three genres associated with the title
 
 - **rating**: Bechdel Test rating (0-3)


Other data used comes from the TidyTuesday social data project through GitHub, found [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-09/readme.md). 

```{r}
movies |> select(title, year, imdb_rating, metascore, budget_2013, binary) |> 
  slice(44:46) |>  knitr::kable() 
```

The code manual for the TidyTuesday data: 

- **year**: release year

- **title**: title of movie

- **binary**: binary Pass or Fail of the Bechdel Test

- **budget_2013**: budget normalized to 2013

- **metascore**: Metascore (critic) rating (0-100)

- **imdb_rating**: IMDb (user) rating (0-10)

data + table(s)

one plot for each 

model code without output

abbr model (latex) 


