---
title: "sentiment analysis"
author: "Hailey Quintavalle"
date: "2023-10-01"
output: html_document
---


```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(stringr)
library(tidyverse)
library(here)
library(tidytext)
library(textdata)
```


```{r}
afinn <- get_sentiments("afinn")
bing <- get_sentiments("bing")
nrc <- get_sentiments("nrc")
```

```{r message=FALSE, warning=FALSE}
# read in the data manually
raw_bechdel <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/raw_bechdel.csv')
movies <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/movies.csv')
```

Create data set where each row is a word and there is a column for each word's sentiment (positive/negative or fear/anger/joy/etc.).

```{r}
movies$plot <- str_to_lower(movies$plot)
plot <- movies %>% select(plot, title) %>% unnest_tokens(output = "word", input = "plot")
plot_stop <- anti_join(plot, stop_words, by = c("word" = "word"))
```



```{r}
plot_afinn <- plot_stop %>% inner_join(afinn)
plot_bing <- plot_stop %>% inner_join(bing)
plot_nrc <- plot_stop %>% inner_join(nrc)



plot_afinn
movie_sentiment <- plot_afinn %>% 
  group_by(title) %>%
  summarise(sentiment_score = sum(value))

plot_nrc %>% head()

plot_nrc <- plot_nrc |> mutate(sentiment = as.factor(sentiment),
                   title = as.factor(title)) |>
  group_by(sentiment, title, .drop = FALSE) |>
  summarise(count_sent = n())
```


```{r}
movies2 <- movies %>% inner_join(movie_sentiment)
movies2 %>% select(title, sentiment_score)
```

```{r}
hist(movies2$sentiment_score) # general overview of all sentiment scores
```

```{r}
movies2 %>% ggplot(mapping = aes(x = factor(binary), y = sentiment_score)) +
  geom_boxplot()
```

```{r}
movies2 %>% ggplot(mapping = aes(x = clean_test, y = sentiment_score, color = clean_test)) +
  geom_boxplot()
```

ok = passes test
dubious = passes test, but still biased
men = women only talk about men
notalk = women don't talk to each other
nowomen = fewer than two women

```{r}
movies_bing <- movies2 %>% inner_join(plot_bing)
movies_nrc <- movies2 %>% inner_join(plot_nrc) 
```

```{r}
movies_bing %>% select(title, sentiment) %>% head()
```

just an example:
```{r}
movies_nrc %>% select(title, sentiment, count_sent) %>% filter(title == "Grown Ups 2")
```




strip plots with geom_jitter()
x = binary
y = created sentiment score from bing
```{r}
movies_bing %>%
  ggplot(. , mapping = aes(x = binary, y = sentiment, color = sentiment)) +
  geom_jitter()
```




```{r}
movies_nrc %>%
  ggplot(. , mapping = aes(x = count_sent, y = binary, color = sentiment)) +
  geom_boxplot() +   # can also do jitter
  facet_wrap(movies_nrc$sentiment) +
  theme(legend.position = "none")
```

```{r}
movies_test <- movies2 %>% select(title, binary)
movies_nrc_test <- plot_nrc %>% inner_join(movies_test) 
```


plot true/false for anger on x-axis and plot pass/fail on axis w/ geom_jitter()

ANGER
```{r}
movies_nrc_test %>% mutate(anger = if_else(sentiment == "anger", TRUE, FALSE)) %>%
  ggplot(. , mapping = aes(x = anger, y = binary, color = binary)) +
  geom_jitter()
```

JOY
```{r}
movies_nrc_test %>% mutate(joy = if_else(sentiment == "joy", TRUE, FALSE)) %>%
  ggplot(. , mapping = aes(x = joy, y = binary, color = binary)) +
  geom_jitter()
```


NEGATIVE
```{r}
movies_nrc_test %>% mutate(negative = if_else(sentiment == "negative", TRUE, FALSE)) %>%
  ggplot(. , mapping = aes(x = count_sent, y = binary, color = count_sent)) +
  geom_jitter()
```



```{r}
movies_nrc_test %>% #mutate(negative = if_else(sentiment == "negative", TRUE, FALSE)) %>%
  ggplot(. , mapping = aes(x = sentiment, y = binary, fill = count_sent)) +
  geom_tile()
```

heat map (or jitter)
geom_tile()
fill = count


```{r}
movies_nrc %>% mutate(count_sent_pass = if_else(count_sent > 0, TRUE, FALSE)) %>% group_by(sentiment, count_sent_pass, binary) %>% summarise(n.count = n()) %>%
  ggplot(. , mapping = aes(x = count_sent_pass, y = binary, fill = n.count)) +
  geom_tile() +
  facet_wrap(~sentiment)
```



```{r}
movies_nrc %>% #mutate(count_sent_pass = if_else(count_sent > 0, TRUE, FALSE)) %>%
  ggplot(. , mapping = aes(x = count_sent_pass, y = binary, fill = sum())) +
  geom_tile()
```


sentiment
count_sent_pass
binary
n.count


```{r}
movies_nrc %>% mutate(count_sent_pass = if_else(count_sent > 0, TRUE, FALSE)) %>% group_by(sentiment, count_sent_pass, binary) %>% summarise(n.count = n()) %>% mutate(row_prop = n.count/)
  ggplot(. , mapping = aes(x = count_sent_pass, y = binary, fill = n.count)) +
  geom_tile() +
  facet_wrap(~sentiment)
```



```{r}
movies_nrc %>% 
  mutate(count_sent_pass = if_else(count_sent > 0, TRUE, FALSE)) %>% 
  group_by(sentiment, count_sent_pass, binary) %>% 
  mutate(binary_pass = if_else(binary == "PASS", 0, 1)) %>%
  summarise(n.count = n(), n.count_sent = sum(count_sent_pass == "FALSE")) #%>% 
  #mutate(row_prop = n.count / n.count_sent) 
```




